The Bot on Speaking Terms: The Effects of Conversation Architecture on Perceptions of Conversational Agents

### 2023-02-21 paper.tex
restructured manuscript

%% Manuscript for the effect of designed conversational architecture on the perception of agents
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,screen,review, anonymous]{acmart}

@@

\author{Young-Ho Kim}
\email{ygho.kim@navercorp.com}
\affiliation{%
  \institution{Naver Corporation}
  \city{Seoul}
  \country{Korea}
}

@@

\section{Introduction}

Conversational agents (CAs), such as Amazon Alexa or Google Assistant, are designed to interact with humans using natural language through voice or text modalities. Since these agents interact with users using natural language, conversation architecture — which refers to what a CA says and how it says it — affects how these agents interact with users. The effectiveness of these interactions with CAs are strongly dependent on users' perceptions of agents \cite{knijnenburg2016inferring}\cite{seeger2021chatbots}. According to previous research, there is a correlation between CAs' conversation architecture and users' perception of these agents.

While there are various studies on how different conversation architecture elements affects agents' perceptions, there is a paucity of knowledge on the overall coverage and effects of these relationships explored in literature. For conversation architecture elements, The use of affective language is commonly explored, with studies finding that conversational agents are perceived as more socially present and emotionally intelligent if they use sentiment-adaptive response based on user's utterances \cite{diederich2019emulating}\cite{yang2017perceived}. Another commonly explored element is the use of prosody in voice-based agents, such as the use of express prosody contributing to higher perceived enjoyment and intimacy with the agent \cite{kim2020can}. However, there is a lack of research to synthesize these findings into an overall framework. One of the possible issues is the lack of clear and consistent definitions on the aspects of user's perceptions of agent and conversation architectural elements.

Currently there is no systematic understanding on the elements of conversation architecture that are relevant to perceptions of agents. Some papers have started to examine the speech specifics that are being explored in literature, such as Clark et al. \cite{clark2019state} capturing different elements of system speech production for voice-based agents and categorizing them based on content, style, and other topics. There are also some investigations of conversation architecture elements within the broader field of studying cues that trigger a social reaction of the user towards the CA. Feine et al's \cite{feine2019taxonomy} paper laid the foundation to create a consistent taxonomy for these social cues. However, there is no comprehensive research specifically for conversation architecture elements that are relevant to user perceptions.

Related to user perceptions, there is also no systematic understanding on the perceptions of agents affected by speech variations. Some research discussed the perceptions of agents as part of the broader scope of user experiences of CAs. These publications have gathered UX dimensions used to evaluate conversational agents, which include the perceptions of agents (e.g. empathy, humanness) alongside other assessments (e.g. physiological data) \cite{clark2019state}\cite{finch2020towards}. Some even categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence \cite{zheng2022ux}. However, these studies are assessing the general field of UX measurements and not specifically on the perceptions of agents, and do not analyze the effects of conversation architecture on these perceptions.

These research gaps discussed above: the paucity of knowledge on synthesizing the effect of speech specifics on perceptions of CAs as well as the lack of systematic understanding on the elements of conversation architecture and perceptions of agents motivated us to the goal of how to design conversation architecture in order to orchestrate perceptions of conversational agents. First, we want to understand \textbf{(RQ1) what perception aspects of agents are being explored in relation to the effects of conversation architecture elements}. While there are various architecture elements of conversation architecture used in a CA's utterances, we don't have a holistic understanding of them. This leads to our second research question: \textbf{(RQ2) what elements of conversation architecture are relevant to the perceptions of agents?} Lastly, we want to understand the effect of conversation architecture on perceptions of agent, specifically: \textbf{(RQ3) what are the relationships between conversation architecture elements and the perceptions of CAs?}

To answer these questions, we performed a comprehensive review on existing literature from 2010 to 2022 and synthesized the effect of conversation architecture elements on the perceptions of CAs based on 57 relevant papers (Figure \ref{fig:heatmap-impact}). We also grouped the perceptions of agents affected by conversation architecture into four categories and eleven aspects (Table \ref{tab:perceptions}), and grouped the speech variations related to perceptions of agents into four categories and eleven elements (Table \ref{tab:cues}). %Lastly, we coded the explored connections between conversation architecture and perceptions and synthesized their relationships into a framework. Through our analysis, we also found that there are inconsistencies in the assessment of perceptions across studies, as well as influencing factors other than conversation architecture that impact the perceptions of agents. 
This work contributes to the HCI community by presenting a framework that demonstrates the effect of conversation architecture on perceptions of conversational agents, as well as taxonomies for perception aspects and conversation architecture elements providing clear and consistent terms that can be used in future research. Together, these contributions move us one step closer to designing CAs that effectively interact with users. 
%Also, our analysis extends existing reviews on UX research of CAs \cite{clark2019state}\cite{rapp2021human}\cite{zheng2022ux} by providing a synthesized framework outlining the relationships between conversation architecture and perceptions of agents. With the help of this framework, we are taking the first step to understand how to design conversational agents to solicit specific social reactions from users.

In the remainder of the paper, we first outline related background work, our literature review process, as well as the characteristics of the papers in our reviewed corpus. Following that, we describe in detail the taxonomy for the perception of agents, the taxonomy for conversation architecture element, as well as the framework on the relationships between perceptions of agents and conversation architecture. Finally, we discuss research challenges and opportunities as well as ethical considerations for designing conversational architecture to orchestrate perceptions of conversational agents.

\section{Literature Review}

* human-human vs. human-AI

* anthropomorphism
%Anthropomorphism is defined as the attribution of traits that we typically associate with being distinctly human to nonhuman entities \cite{waytz2010sees}. For example, users tend to personify conversational agents like Amazon Alexa by using person pronouns instead of object pronouns in online reviews \cite{purington2017alexa}.  Research shows that anthropomorphic design is beneficial to establishing and maintaining trust between users and conversational agents \cite{seeger2021chatbots}. Also, speakers tend to align their lexical choices with conversational agents, similar to human-human conversations \cite{cowan2015does}. Anthropomorphism has been shown to ease user interactions, e.g. making agents more approachable, engaging, and trustworthy when they exhibit human characteristics \cite{qiu2009evaluating}. These processes are of particular interest for human-agent communication because they form the basis for user expectations and predispositions regarding agents' behavior, reliability of the information, etc. \cite{kuzminykh2020genie}.

* how to synthesize

* user experience evaluations of conversational agents
%Other papers categorized CA assessments into themes. For example, Rapp et al. \cite{rapp2021human} generated themes related to how users' experience with chatbots such as experiencing the chatbot including assessments on expectation, perception, satisfaction etc.  Most recently, Zheng et al's literature review on the UX research of CAs \cite{zheng2022ux} categorized the metrics based on the type of method used, including technical measures like system error rate and perception measures like perceived social presence. However, existing studies use different terminologies and categories across aspects of perception. As an illustration, it is unclear if the theme of experiencing the chatbot from Rapp et al. \cite{rapp2021human} contains similar aspects to the perception towards CA in Zheng et al \cite{zheng2022ux}'s analysis.
%\cite{finch2020towards} Towards unified dialogue system evaluation: A comprehensive analysis of current evaluation protocols

\section{Methods}

This section describes the research methodologies used for data collection and data analysis. Additionally, it presents the characteristics of the papers in our reviewed corpus.

\subsection{Data Collection}

Following PRISMA guidelines \cite{prisma}, we reviewed and selected literature exploring the relationship between the specifics of conversation architecture elements and perceptions of CAs. Searches were carried out in the ACM Digital Library between January 1 and January 15, 2023. Through our analysis, we didn't find any common terms used to refer to either conversation architecture elements, or aspects of perceptions. As such, we generalized our search term to capture articles related to conversational agents. Based on search terms used in previously published literature reviews \cite{clark2019state}\cite{rapp2021human}, the following keywords are used to search for publications related to conversational user interfaces:
\newline

\textit{"conversational agent" OR "natural language interface" OR "IPA" OR "intelligent personal assistant" OR "chatbot" OR "speech interface" OR "voice assistant" OR "intelligent agent" OR "human-chatbot communication" OR "virtual agent" OR "dialog* system" OR "voice user interface" OR "human computer dialog*"}
\newline

The following selection criteria are applied to identify literature related to the effect of conversational architecture on the perception of agents:
\begin{itemize}
  \item The paper was published between 2010 and 2022.
  \item The paper is peer-reviewed and written in English.
  \item The paper contains the use of voice-based or text-based conversational agents.
  \item The paper contains studies on the impact of conversation architecture elements on the perceptions of agents.
  \item The paper contains impact of conversation architecture elements can be separated from other effects (e.g. embodiment).

\end{itemize}

The initial query retrieved 2901 unique publications. We screened the titles and abstracts of the papers based on the selection criteria above, resulting in 221 papers. The fully body of these papers are then reviewed, selecting papers that met the criteria. A search for additional literature was also performed to supplement the corpus, adding 8 more papers to the selection. In total, we identified 57 relevant articles for analysis (see Figure \ref{fig:prisma}).

\begin{figure}[h]
  \centering
  \includegraphics[width=1\columnwidth]{fig-prisma.png}
  \caption{Literature search using PRISMA guidelines}
  \label{fig:prisma}
\end{figure}

\subsubsection*{Literature Corpus Characteristics}

The papers reviewed (n=57) were published between May 2011 and November 2022. More than 75\% of the papers were published in or after 2019, with a slight trend upwards over the years (see Figure \ref{fig:paper}). The vast majority of the papers in our corpus were published in conference proceedings (n=50), with the remainder papers published in journals. Out of the papers published in conferences, the top conferences were The ACM Conference on Human Factors in Computing Systems\footnote{https://dl.acm.org/conference/chi} (n=16), Conversational User Interfaces\footnote{https://dl.acm.org/conference/cui} (n=7), Human-Agent Interaction\footnote{https://dl.acm.org/conference/hai} (n=4), and Intelligent Virtual Agents\footnote{https://dl.acm.org/conference/iva} (n=4). 
%Out of the papers published in journals, some venues include the International Journal of Human-Computer Interaction\footnote{https://www.tandfonline.com/journals/hihc20} (n=2) and Interacting with Computers\footnote{https://academic.oup.com/iwc} (n=1).

On the modality characteristics of the conversational agents in the corpus, there is a roughly even split between the modalities, with slightly more papers exploring voice-based CAs (n=30) compared to text-based CAs (n=27).

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{fig-paper.png}
  \caption{Number of papers by year}
  \label{fig:paper}
\end{figure}

\subsection{Data Analysis}

\subsubsection*{Perceptions of Agents} To understand the perceptions of agents related to conversation architecture (RQ1), assessments for the perceptions of agents were extracted from each paper. We used inductive thematic analysis to group these assessments into codes based on their meanings. For example, the code likeability of the agent contains the questionnaire item "this voice agent was likeable" used by \cite{cuadra2021my}\cmt{[67]}, Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed}'s set of questions on likeability used by \cite{linnemann2018can}\cmt{[15]}, and Subjective Assessment of Speech System Interface (SASSI) questionnaire \cite{hone2000towards}\cmt{sassi}'s set of questions on likeability used by \cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}. This step resulted in 83 unique codes. These codes are then organized based similarity of the meanings, resulting in 11 aspects of perceptions. For example, the aspect of personality traits of the agent contains measurements such as likeability, funniness, and kindness. Lastly, the 11 aspects are grouped into 4 categories: perception of interaction with agent, perception of agent's ability, perception of sociability with agent, and perception of agent's humanness (Table \ref{tab:perceptions}).

\subsubsection*{Conversation Architecture Elements}
As to the elements of conversation architecture that are relevant to the perception of agents (RQ2), we extracted the specifics of conversation architecture used in each paper. Some of the papers used multiple features in their CA design, such as the the anthropomorphic agent used in Seeger et al's study \cite{seeger2021chatbots}\cmt{[35]}. In these composite situations, we broke them down into their individual features. For example, the anthropomorphic agent \cite{seeger2021chatbots}\cmt{[35]} was separated into emotional expressions, is-typing indicator, emoticons, and response delay and captured as codes. 58 unique codes were created as part of this process, capturing features like sentiment-adaptive responses \cite{diederich2019emulating}\cmt{[25]}, lexical alignment \cite{spillner2021talk}\cmt{[18]}, and typos \cite{westerman2019believe}\cmt{[9]}. We then organized these codes into elements based on similarity, resulting in 12 elements of conversation architecture. For example, the element of disfluency contains fillers \cite{jeong2019exploring}\cmt{[10]}\cite{wester2015artificial}\cmt{[14]}, interjections \cite{ceha2022expressive}\cmt{[77]}\cite{hu2021enhancing}\cmt{[56]}, repetitions \cite{yang2021effect}\cmt{[72]} and typos \cite{westerman2019believe}\cmt{[9]}. These elements are grouped into 4 categories: dialog strategy, content affectiveness, content style, and speech format (Table \ref{tab:cues}).

\subsubsection*{Relationship Between Perceptions of Agents and Conversation Architecture}
To study the effect of conversation architecture on users' perceptions (RQ3), we extracted the connections explored in each paper, using the perception aspects and conversation architecture elements developed in the previous data analysis steps. Each connection's effect was also recorded based on whether an association was found in the study and the nature of that association. Out of our review corpus, 265 connections between perceptions of agents and conversation architecture were explored in literature. To analyze the specifics of conversation architecture that affect the perceptions of CAs, 72 connections that did not result in observed relationships were discarded, resulting in 193 relationships for analysis. For example, the connection between the matching style of a CA and user satisfaction was removed because Hoegen et al. \cite{hoegen2019end}\cmt{[31]} did not find a significant difference between the style matching agent and the non-style matching agent for overall interaction satisfaction. Out of the 193 relationships, 10 were relationships based on agents modifying multiple architecture elements (e.g. \cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2021manipulating}\cmt{[68]}). They were not included in the final framework as we could not attribute the perceptions of agents to the underlying core elements. Overall, 183 relationships between individual architecture elements and perceptions of agents are incorporated into our synthesized framework, visualized as a heatmap to demonstrate their relationships with each other (Figure \ref{fig:heatmap-impact}).

\section{Findings}

\begin{figure*}[]
  \centering
  \includegraphics[width=\textwidth]{fig-heatmap-impact.png}
  \caption{Heatmap of literature for perception of conversational agents for each type of conversational architecture element}
  \label{fig:heatmap-impact}
\end{figure*}

\subsection{Perceptions of Agents}

As shown in Table \ref{tab:perceptions}, there are four categories defined for the perceptions of conversational agents covering 11 different aspects of perception. The details of each category and aspect are discussed below.

\textbf{Perception of interaction with agent} assesses the overall interaction quality users had with the conversational agent. The three aspects for this perceptions are usability, engagement and satisfaction. \textit{Usability} captures the utilitarian component of the interaction, whether it was accurate, easy to use, efficient or helpful. Some commonly used methods to evaluate usability include the response accuracy portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, or the NASA Task Load Index (NASA-TLX) \cite{hart1988development}\cmt{nasa} for cognitive workload. Questions such as "the system is easy to use" or "it is easy to understand the agent" are also used to evaluate usability. \textit{Engagement} on the other hand captures users' emotional reactions to the CA, whether they have enjoyed the conversation, or annoyed or frustrated with the interaction. Some commonly used methods to evaluate engagement include the annoyance portion of the SASSI questionnaire \cite{hone2000towards}\cmt{sassi}, and the Use Engagement Scale (UES) \cite{o2018practical}\cmt{ues}. Questions such as "I enjoyed using the system" or "I felt frustrated with the agent" are also used to evaluate engagement. Lastly, \textit{Satisfaction} captures users' overall satisfaction interacting with the agent. Questions such as "the overall assessment of conversing with the CA was satisfactory" are used to evaluate this perception.

\textbf{Perception of agent's ability} assesses the perceived capabilities of the agent. Unlike system capabilities that affect agent's performance, the perceived ability category captures perceptions of agents with equivalent system capabilities but varied conversation architecture elements. Specifically, \textit{intelligence} captures the agent's expertise and knowledge, and it is commonly administered through the Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} using the set of questions related to perceived intelligence. Also survey questions such as asking users about the agent's intelligence and domain knowledge are used to evaluate perceived intelligence. \textit{Competence} takes intelligence one step further by examining the agent's ability to put its intelligence into practice. Surveys or qualitative feedback are usually used to assess if the agent is capable and competent, and whether users have confidence in the agent's ability to get the job done. Lastly, \textit{credibility} captures agent's truthfulness, benevolence, and user's confidence in CAs. Some commonly used methods to evaluate trust include the Trust Propensity Scale \cite{mayer1999effect} and the Individualized Trust Scale (ITS) \cite{wheeless1977measurement}. Questions such as "is the agent honest" and "can I trust the agent with sensitive information" are also used to evaluate trust.

\textbf{Perception of the sociability with agent} assesses the emotional connections that users have with agents. This category includes perception aspects of conversation tone, social presence and intimacy. \textit{Conversation tone} captures the affective impression of the agent's tone, such as empathy and expressiveness. Also, this aspect includes whether the tone used by the agent was perceived as friendly, polite or warm. \textit{Social presence} captures the sense of connectness and psychological distance users have with an agent. Some aspects in this category include the sense of familiarity or similarity with the agent, and whether users feel the agent behaves like them or have similar attitudes to them. The category of \textit{Intimacy} extends social presence into the realm of the quality of relationships with an agent. Some commonly used methods to assess intimacy include the set of social attraction questions from the interpersonal attraction questionnaire \cite{mccroskey1975development} and the quality of relationship inventory (QRI) \cite{pierce1997assessing}. These questionnaires include questions like "I think the agent could be a friend of mine", or "I feel we could establish a personal relationship with each other".

\textbf{Perception of agent's humanness} assesses the specifics of anthropomorphized perceptions of conversational agents. \textit{Human-likeness} captures whether the agent presented itself as natural and human-like, or artificial and machine-like. The Godspeed questionnaire \cite{bartneck2009measurement}\cmt{godspeed} set of questions related to anthropomorphism and the Ascent of Man scale \cite{kteily2015ascent} are commonly used methods to evaluate human-likeness. Survey questions with semantic scales such as "human-like / machine-like" and "artificial / natural" are also commonly used for this aspect of perception. \textit{Personality traits} captures the human characteristics that are attributes to the agent. This is commonly collected as qualitative feedback from users, commenting on whether the agent is extroverted or introverted, or the perceived personality such as likeable, funny or witty. Sometimes the Big-5 personality traits questionnaire \cite{gosling2003very} is used to map an agent's disposition on various personality dimensions.

Overall there is a good coverage of different aspects of perception based on the list of papers reviewed in our corpus. The most commonly explored aspect categories is the perception the interaction with agent, followed by the perception of agent's humanness. There are two aspects that are the least explored compared to the others relationships: competence within the perception of agent's ability, and intimacy within the perception of social connection with agent. This may be due to the controlled lab settings for the experiments, where participants are given the scenarios for interaction. This type of environment is not conducive to forming relationships with a conversational partner, as noted by Linnerman et al. in their discussions \cite{linnemann2018can}\cmt{[15]}. The same factor could impact the assessment of agent's competence, as the users may not feel like they have the expertise to assess their perceptions. 
%These factors could contribute to the reasons why competency and intimacy are not as frequently measured in experimental studies.

\begin{table*}[ht]
\renewcommand*{\arraystretch}{1.4}
\resizebox{\textwidth}{!}{%
\begin{tabular}{@{}p{0.17\textwidth} | p{0.12\textwidth} | p{0.20\textwidth} | >{\centering}p{0.09\textwidth} | p{0.42\textwidth} @{}}
%!{\vrule width 1.2pt} 
\Xhline{1.2pt}
\multicolumn{2}{l|}{\textbf{Perception Aspects}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers} 
\\ \Xhline{1.2pt}
\multirow{3}{*}{\parbox{0.17\textwidth}{Perception of \newline Interaction with Agent}}
    & Usability & accuracy, ease of use, \newline efficiency, helpfulness & 23 
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2022expressive}\cmt{[77]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{elsholz2019exploring}\cmt{[61]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{kim2020can}\cmt{[24]}
    \cite{kraus2020effects}\cmt{[64]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{misu2011toward}\cmt{[83]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{wilhelm2022keep}\cmt{[28]}
\\ \cline{2-5}
    & Engagement & enjoyment, annoyance, \newline desirable, intention to use  & 28
    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{elsholz2019exploring}\cmt{[61]}\cite{fadhil2018effect}\cmt{[52]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{healey2013relating}\cmt{[39]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2020can}\cmt{[24]}\cite{kim2019comparing}\cmt{[89]}
    \cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{miehle2018exploring}\cmt{[51]}\cite{miyamoto2017improving}\cmt{[46]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2022user}\cmt{[75]}\cite{xiao2021let}\cmt{[73]}\cite{yang2021effect}\cmt{[72]}\cite{zhu2022effects}\cmt{[26]}    
\\ \cline{2-5}
    & Satisfaction & service satisfaction, quality of interaction & 12
    & \cite{ceha2022expressive}\cmt{[77]}\cite{choi2020nobody}\cmt{[54]}\cite{diederich2019emulating}\cmt{[25]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{gnewuch2018faster}\cmt{[19]}\cite{hoegen2019end}\cmt{[31]}\cite{hu2022polite}\cmt{[76]}\cite{ma2022ask}\cmt{[29]}\cite{roy2021users}\cmt{[71]}\cite{wilhelm2022keep}\cmt{[28]}\cite{yang2017perceived}\cmt{[44]}
\\ \Xhline{1.2pt} 
\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of Agent's Ability}}
    & Intelligence & knowledgeable, intelligent, expertise & 11
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{feijoo2021effects}\cmt{[70]}\cite{hu2021enhancing}\cmt{[56]}\cite{jeong2019exploring}\cmt{[10]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]} 
\\ \cline{2-5}
    & Competence & competent, appropriate & 6 
    & \cite{cox2022does}\cmt{[27]}\cite{kraus2020effects}\cmt{[64]}\cite{jestin2022effects}\cmt{[81]}\cite{lee2019s}\cmt{[55]}\cite{misu2011toward}\cmt{[83]}\cite{westerman2019believe}\cmt{[9]}
\\ \cline{2-5}
    & Trust & credibility, trustworthy, truthfulness, confidence & 15
    & \cite{andrews2012system}\cmt{[38]}\cite{chan2021kinvoices}\cmt{[74]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{fadhil2018effect}\cmt{[52]}\cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{jestin2022effects}\cmt{[81]}\cite{kraus2020effects}\cmt{[64]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{ma2022ask}\cmt{[29]}\cite{seeger2021chatbots}\cmt{[35]}\cite{tolmeijer2021female}\cmt{[62]}\cite{wilhelm2022keep}\cmt{[28]}    
\\ \Xhline{1.2pt} 
\multirow{3}{*}{\parbox{0.16\textwidth}{Perception of \newline Sociability with Agent}}
    & Conversation Tone & friendly, warm, empathetic, persuasive & 20 
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cox2022does}\cmt{[27]}\cite{cuadra2021my}\cmt{[67]}\cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{dubiel2020persuasive}\cmt{[60]}\cite{healey2013relating}\cmt{[39]}\cite{hu2021enhancing}\cmt{[56]}\cite{hu2022polite}\cmt{[76]}\cite{jestin2022effects}\cmt{[81]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2019s}\cmt{[55]}\cite{miehle2018exploring}\cmt{[51]}
    \cite{moilanen2022measuring}\cmt{[82]}\cite{tolmeijer2021female}\cmt{[62]}\cite{yang2021effect}\cmt{[72]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}
    & Social Presence & connectedness, familiarity, psychological distance & 18
    & \cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cuadra2021my}\cmt{[67]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{lubold2016effects}\cmt{[86]}
    \cite{ma2022ask}\cmt{[29]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{westerman2019believe}\cmt{[9]}    
\\ \cline{2-5}
    & Intimacy & intimate, rapport, quality of relationship & 7 
    & \cite{choi2020nobody}\cmt{[54]}\cite{khooshabeh2011does}\cmt{[37]}\cite{kim2020can}\cmt{[24]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{lubold2016effects}\cmt{[86]}\cite{westerman2019believe}\cmt{[9]}
\\ \Xhline{1.2pt}
\multirow{2}{*}{\parbox{0.16\textwidth}{Perception of Agent's Humanness}}
    & Human-likeness & human-like, natural, \newline artificial, machine-like & 20
    & \cite{ashktorab2019resilient}\cmt{[88]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{choi2020nobody}\cmt{[54]}\cite{cox2022does}\cmt{[27]}\cite{diederich2019emulating}\cmt{[25]}\cite{gnewuch2018faster}\cmt{[19]}\cite{haas2022keep}\cmt{[78]}\cite{hu2022polite}\cmt{[76]}\cite{jeong2019exploring}\cmt{[10]}\cite{jestin2022effects}\cmt{[81]}\cite{lubis2019positive}\cmt{[43]}\cite{ma2022ask}\cmt{[29]}\cite{misu2011toward}\cmt{[83]}\cite{niewiadomski2013laugh}\cmt{[85]}
    \cite{ouchi2019should}\cmt{[59]}\cite{seeger2021chatbots}\cmt{[35]}\cite{wester2015artificial}\cmt{[14]}\cite{westerman2019believe}\cmt{[9]}\cite{zhu2022effects}\cmt{[26]}    
\\ \cline{2-5}
    & Personality Traits & likeable, kind, witty, funny, creepy & 20
    & \cite{andrews2012system}\cmt{[38]}\cite{ceha2022expressive}\cmt{[77]}\cite{ceha2021can}\cmt{[57]}\cite{chan2021kinvoices}\cmt{[74]}\cite{cuadra2021my}\cmt{[67]}\cite{haas2022keep}\cmt{[78]}\cite{habler2019effects}\cmt{[63]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{huiyang2022improving}\cmt{[17]}\cite{jeong2019exploring}\cmt{[10]}\cite{kim2019comparing}\cmt{[89]}\cite{lee2020hear}\cmt{[23]}\cite{linnemann2018can}\cmt{[15]}\cite{miehle2018exploring}\cmt{[51]}
    \cite{ouchi2019should}\cmt{[59]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}\cite{wester2015artificial}\cmt{[14]}\cite{zhu2022effects}\cmt{[26]} 
\\ \Xhline{1.2pt}
\end{tabular}%
}
\caption{Perception aspects}
\label{tab:perceptions}
\end{table*}

\begin{table*}[h]
\resizebox{\textwidth}{!}{
\renewcommand*{\arraystretch}{1.4}
\begin{tabular}{@{}p{0.17\textwidth} | p{0.14\textwidth} | p{0.25\textwidth} | >{\centering}p{0.09\textwidth} | p{0.34\textwidth} @{}}
\Xhline{1.2pt}
\multicolumn{2}{l|}{\textbf{Conversation Architecture Elements}} & \textbf{Examples} & \textbf{No. Papers} & \textbf{Papers}
\\ \Xhline{1.2pt}
\multirow{3}{*}{Dialog Strategy} & Social Dialog & social talk, self-disclosure  & 7
& \cite{andrews2012system}\cmt{[38]}\cite{lee2020hear}\cmt{[23]}\cite{lubold2016effects}\cmt{[86]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}

& Initiative & proactive dialogue, conversation \newline repair & 4
& \cite{ashktorab2019resilient}\cmt{[88]}\cite{cuadra2021my}\cmt{[67]}\cite{kraus2020effects}\cmt{[64]}\cite{xiao2021let}\cmt{[73]}
\\ \cline{2-5}

& Response Delay & response delay, typing indicator & 4
& \cite{gnewuch2018faster}\cmt{[19]}\cite{gnewuch2018chatbot}\cmt{[21]}\cite{gnewuch2022opposing}\cmt{[20]}\cite{seeger2021chatbots}\cmt{[35]}
\\ \Xhline{1.2pt}

\multirow{2}{*}{Content Affectiveness} & Affective Language & emotional expressions, sentiment-adaptive responses & 11
& \cite{daher2020empathic}\cmt{[58]}\cite{diederich2019emulating}\cmt{[25]}\cite{healey2013relating}\cmt{[39]}\cite{hu2022polite}\cmt{[76]}\cite{lee2019s}\cmt{[55]}\cite{lubis2019positive}\cmt{[43]}\cite{moilanen2022measuring}\cmt{[82]}\cite{seeger2021chatbots}\cmt{[35]}\cite{volkel2022user}\cmt{[75]}\cite{yang2017perceived}\cmt{[44]}\cite{zhu2022effects}\cmt{[26]}
\\ \cline{2-5}

& Humour & humorous content, jokes & 6
& \cite{ceha2021can}\cmt{[57]}\cite{go2021conversational}\cmt{[80]}\cite{khooshabeh2011does}\cmt{[37]}\cite{miyamoto2017improving}\cmt{[46]}\cite{niewiadomski2013laugh}\cmt{[85]}\cite{volkel2021manipulating}\cmt{[68]}
\\ \Xhline{1.2pt}

\multirow{3}{*}{Content Style} & Formality & formal vs. casual, honorific \newline expressions & 9
& \cite{cox2022does}\cmt{[27]}\cite{elsholz2019exploring}\cmt{[61]}\cite{habler2019effects}\cmt{[63]}\cite{jestin2022effects}\cmt{[81]}\cite{kim2019comparing}\cmt{[89]}\cite{ma2022ask}\cmt{[29]}\cite{moilanen2022measuring}\cmt{[82]}\cite{ouchi2019should}\cmt{[59]}\cite{volkel2022user}\cmt{[75]}
\\ \cline{2-5}

& Alignment & content matching, lexical \newline alignment, agreeableness & 7
& \cite{healey2013relating}\cmt{[39]}\cite{hoegen2019end}\cmt{[31]}\cite{huiyang2022improving}\cmt{[17]}\cite{linnemann2018can}\cmt{[15]}\cite{spillner2021talk}\cmt{[18]}\cite{volkel2021examining}\cmt{[69]}\cite{volkel2021manipulating}\cmt{[68]}
\\ \cline{2-5}

& Elaborateness & elaborate, concise, sentence \newline structure & 6
& \cite{haas2022keep}\cmt{[78]}\cite{miehle2018exploring}\cmt{[51]}\cite{moilanen2022measuring}\cmt{[82]}\cite{roy2021users}\cmt{[71]}\cite{volkel2021manipulating}\cmt{[68]}\cite{volkel2022user}\cmt{[75]}
\\ \Xhline{1.2pt}

>>>>

%% Manuscript for the effect of designed conversational architecture on the perception of agents
%%
%% The first command in your LaTeX source must be the \documentclass command.
\documentclass[sigconf,screen,review, anonymous]{config/acmart}

@@

\author{Young-Ho Kim}
\email{yghokim@younghokim.net}
\affiliation{%
  \institution{NAVER AI Lab}
  \country{Republic of Korea}
}

@@

\input{sections/1-introduction}
\input{sections/2-related_work}
\input{sections/3-method}
\input{sections/4-findings}
\input{sections/5-discussion}
\input{sections/6-conclusion}
